{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-06 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

                    F(x_0) - F(x^+) + \frac{L_0\alpha_0}{2} \Vert x^+ - v_k\Vert^2

@@

                    \prod_{i = 0}^{k - 1} (1 - \alpha_{i + 1})
                    \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right)

@@

@@

@@

            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 

@@

                \Vert \mathcal G_{L_k} y_k\Vert &\le 

@@

@@

        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\\vspace{-1em}

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{Restarting with function values}
    \section{Applying them to large scale LP}
    \section{Nonconvex convergence}

>>>>

                    F(x_0) - F(x^+) + \frac{L_0\alpha_0}{2} \Vert x^+ - v_0\Vert^2

@@

                \frac{\beta_kL_0}{2}\Vert x^+ - x_{-1}\Vert^2. 

@@

                &\hspace{-0.3em}\underset{\text{(iii)}}{\le} 

@@

                &\hspace{-0.3em}\underset{\text{(iv)}}{\le} 

@@

            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 

@@

                \Vert \mathcal G_{L_k} (y_k)\Vert &\le 

@@

        \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\
            Suppose that the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, it satisfies $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 
            Suppose that $(\beta_k)_{k \ge 0}$ is a sequence such that $\beta_0 = 1$ and for all $k \ge 1$ it's defined as: 
            If, we set $\rho_{k - 1} = L_{k}^{-1}L_{k - 1}$ such that $L_k >0$ for all $k \ge 1$, then for all $k \ge 1$ it has the inequality: 
                \beta_k \le \left(
                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{L_i^{-1}}
                \right)^{-2}. 
            We state the following intermediate results needed to construct the proof. 
            They will be proved at the end. 
                \item[(a)] $(\beta_k)_{k \ge 0}$ is monotone decreasing and it's strictly larger than zero. 
                \item[(b)] Because $\rho_{k}L_{k + 1}L_k = 1$ for all $k \ge 0$, the definition of $(\beta_k)_{k\ge 0}$ simplifies and $\beta_k = (\alpha_k^2/\alpha_0^2)(L_k/L_0)$. As a consequence it also gives for all $k \ge 1$ that: 
                    \alpha_k^2 &= \alpha_0^2\beta_kL_0L_k^{-1},
                    \alpha_k &= 1 - \beta_k / \beta_{k - 1}. 
            Starting with results (b), and combine the two equality it gives for all $k \ge 1$ the equality 
                0 &=
                (1 - \beta_k/\beta_{k - 1})^2 - \alpha_0^2L_0L_k^{-1}\beta_k 
                0 &= 
                (1 - \beta_k/\beta_{k - 1}) - \alpha_0\sqrt{L_0L_k^{-1}\beta_k}
                0 &= 
                (\beta_k^{-1} - \beta_{k - 1}^{-1}) - \alpha_0 \sqrt{L_0 L_k^{-1}\beta_k^{-1}}
                &= \left(
                    \sqrt{\beta_k^{-1}} + \sqrt{\beta_{k - 1}^{-1}}
                    \sqrt{\beta_k^{-1}} - \sqrt{\beta_{k - 1}^{-1}}
                - \alpha_0 \sqrt{L_0L_k^{-1}\beta_k^{-1}}
                &\underset{\text{(a)}}{\le} 
                2\sqrt{\beta_k^{-1}}\left(
                    \sqrt{\beta_k^{-1}} - \sqrt{\beta_{k - 1}^{-1}}
                \right) - \alpha_0 \sqrt{L_0L_k^{-1}\beta_k^{-1}}
                2\left(
                    \sqrt{\beta_k^{-1}} - \sqrt{\beta_{k - 1}^{-1}} 
                \right) - \alpha_0 \sqrt{L_0L_k^{-1}}. 
            Since this is true for all $k \ge 1$, taking a telescoping sum of the above series gives
                    \sum_{i = 1}^{k} \sqrt{\beta_i^{-1}} - \sqrt{\beta_{i - 1}^{-1}}
                - \sum_{i = 1}^{k} \frac{\alpha_0}{2} \sqrt{L_0L_k^{-1}}
                \sqrt{\beta_k^{-1}} - \sqrt{\beta_0^{-1}} 
                - \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{ L_k^{-1}}
                \sqrt{\beta_k^{-1}} - 1
                - \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{ L_k^{-1}}. 
            Therefore, transforming the inequality it has: 
                \beta_k &\le 
                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{ L_k^{-1}}
                \right)^{-2}. 
            \textbf{Let's now justify (a)}.
            When $\rho_{i} = L_{i + 1}L_i^{-1}$, the big product simplifies and, it has: 
                \beta_k &= \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) 
                = (1 - \alpha_k)\beta_{k - 1}. 
            Since $\alpha_k \in (0, 1)$, $\beta_k$ is monotonically decreasing. 
            \textbf{To see (b)}, it has from the above which also justifies $1 - \alpha_k = \beta_k / \beta_{k - 1}$. 
            Recall that sequence $(\alpha_k)_{k \ge 0}$ has $\forall k \ge 1$ that $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$, using it we can simplify the product for $\beta_k$, it follows that 
                \beta_k &= \prod_{i = 0}^{k - 1}\left(
                    1 - \alpha_{i + 1}
                \prod_{i = 1}^{k}\alpha_i^2\alpha_{i - 1}^{-2}\rho_{i - 1}^{-1}
                \prod_{i = 1}^{k}\alpha_i^2\alpha_{i - 1}^{-2} L_i^{-1}L_{i - 1}
                &= \left(
                    \frac{\alpha_k^2\alpha_{k - 1}^2\ldots \alpha_1^2}
                    {\alpha_{k -1}^2\alpha_{k - 2}^2\ldots \alpha_0^2}
                    \frac{L_kL_{k - 1}\ldots L_1}{L_{k - 1}L_{k - 1}\ldots L_0}
                = \frac{\alpha_k^2}{\alpha_0^2}\frac{L_k}{L_0}. 
            Rearranging it gives: $\alpha_0^2L_0 \beta_kL_k^{-1} = \alpha_k^2$.
            A simpler upper bound is more useful in practice. 
            For all $k \ge 1$ let $\hat L = \max_{i = 0, 1, \ldots, k} L_k$ then 
                &\le \left(
                    1 + 
                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}}
                \right)^{-2}
                \le \left(
                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}}
                \right)^{-2}
                &= \left(
                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}}}{2}
                \right)^{-2} = L^{-1}_0\hat L\left(
                    \sqrt{L_0^{-1}\hat L} + \frac{k\alpha_0}{2}
                \right)^{-2}
                L^{-1}_0\hat L\left(
                    1 + \frac{k\alpha_0}{2}
                \right)^{-2} 
                = \frac{4\hat L}{L_0(2 + k \alpha_0)^2}. 
            This simplifies the convergence claim back in Theorem \ref{thm:gmapg-ls-convergence}. 
        \begin{theorem}[specialized GMAPG convergence rate]

@@

        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
            The following is (2.2.32) in Nesterov's book, phrased in our GMAPG framework. 

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function.

    \section{Restarting with function values}
    \section{Applying them to large scale LP}
    \section{Nonconvex convergence}
